A Short and Mechanized Consistency Proof for Dependent Type Theory

### 2023-12-19 paper/paper.tex
Add a paragraph to STLC LR proof

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{A Short and Mechanized Consistency Proof for a Dependent Type Theory}

@@

\section{Review of Proof by Logical Relation}
\label{sec:logrelstlc}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{A Short and Mechanized Consistency Proof for Dependent Type Theory}

@@

\section{Review of Proof by Logical Relation}
\label{sec:logrelstlc}
In this section, we give a quick review of the consistency proof of the
simply typed lambda calculus augmented with the empty type through
proof by logical relation.

We give the full specification of the simply typed calculus in
Figure~\ref{fig:stlcsyntax},\ref{fig:stlctyping},\ref{fig:stlcdynamics}
without any further explanation since it is standard.

The goal here is to show that the empty type cannot be
inhabited. A naive attempt at proof by structural induction
